\section{Can I Kick It? / (A Tribe Called Quest)}\label{sec:can_i_kick_it_}
<h3>Intro</h3>
Riff over \upchord{C}and \upchord{F]
&nbsp;
Can I \upchord{C}kick it? (yes, you can!), can I \upchord{F}kick it? (yes,
you can!) (x3)
Can I \upchord{C}kick it? (yes, you can!), Well, I'm \upchord{F}gone
&nbsp;
Can I \upchord{C}kick it? To all the people who can quest like a
\upchord{F}tribe does
Before this, did you really know what \upchord{C}live was?
Comprehend to the track, for it's why \upchord{F}cuz
Getting' measures on the tip of the \upchord{C}vibers
Rock and roll to the beat of the \upchord{F}funk fuzz
Wipe your feet really good on the \upchord{C}rhythm rug
If you feel the urge to freak, do the \upchord{F}jitterbug
Come and spread your arms if you really \upchord{C}need a hug
Afrocentric living is a \upchord{F}big shrug
A life filled with (*PARP*) that's what \upchord{C}I love
A lower plateau is what \upchord{F}were above
If you diss us, we wont even \upchord{C}think of
Will Nipper the doggy give a \upchord{F}big shove?
This rhythm really fits like a \upchord{C}snug glove
Like a box of positives is a \upchord{F}plus, love
As the tribe flies high like a \upchord{C}dove
&nbsp;
<h3>Instrumental</h3>
\upchord{C}\upchord{F}\upchord{C}\upchord{G]
<h3>Instrumental</h3>
Riff over \upchord{C}and \upchord{F]
&nbsp;
Can I \upchord{C}kick it? (yes, you can!), can I \upchord{F}kick it? (yes,
you can!) (x3)
Can I \upchord{C}kick it? (yes, you can!), Well, I'm \upchord{F}gone
Can I \upchord{C}kick it? to my tribe that flows in \upchord{F}layers
Right now, Phife is a poem \upchord{C}sayer
At times, I'm a studio con- \upchord{F}-veyor
Mr. Dinkins, would you please be my \upchord{C}mayor?
You'll be doing us a really big \upchord{F}favour
Boy this track really has a lot of \upchord{C}flavour
When it comes to rhythms, Quest is your \upchord{F}saviour
Follow us for the funky be- \upchord{C}-haviour
Make a note on the rhythm we \upchord{F}gave ya
Feel free, drop your pants, check your \upchord{C}ha-ir
Do you like the garments that we \upchord{F}wear?
I instruct you to be the o- \upchord{C}-beyer
A rhythm recipe that you'll \upchord{F}savour
Doesn't matter if you're minor or \upchord{C}major
Yes, the tribe of the game, rhythm \upchord{F}player
As you inhale like a breath of fresh \upchord{C}air
&nbsp;
Can I \upchord{C}kick it? (yes, you can!), can I \upchord{F}kick it? (yes,
you can!) (x3)
Can I \upchord{C}kick it? (yes, you can!), Well, I'm \upchord{F}gone
&nbsp;
&nbsp;
<h3>Instrumental</h3>
<p>Riff over [C] and [F]</p>
