\section{Mother What'll I do Now? / (George Formby)}\label{sec:mother_what_ll_i_do_now_}
\upchord{C}Mother you give good advice, \upchord{G7}always you mean well
\upchord{C}Now I \upchord{E7}need it \upchord{Am}more than ever \upchord{D7}I'm inside
this \upchord{G7}cell
&nbsp;
\upchord{C}I'm be- \upchord{A7}-hind a \upchord{Dm}prison \upchord{G7}wall
the \upchord{C}bed's too \upchord{A7}hard and \upchord{D7}much too \upchord{G7}small
There's \upchord{C}no py- \upchord{C7}-jamas \upchord{F}here at \upchord{Ab7}all
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
They \upchord{C}told me \upchord{A7}they would \upchord{Dm}treat me \upchord{G7}well
\upchord{C}Tucked in- \upchord{A7}-side my \upchord{D7}little \upchord{G7}cell
But \upchord{C}up to \upchord{C7}now it's \upchord{F}been like \upchord{Ab7}Hell
\upchord{G7}Mother what'll I do \upchord{C}now?
&nbsp;
We're \upchord{C7}parted from each other, \upchord{F}and that's too bad
\upchord{D7}You're my favourite mother, oh the best I ever \upchord{G7}had
&nbsp;
To- \upchord{C}-night I've \upchord{A7}got a \upchord{Dm}date you \upchord{G7}see
but \upchord{C}they won't \upchord{A7}let me \upchord{D7}have a \upchord{G7}key
And the \upchord{C}warders \upchord{C7}won't wait \upchord{F}up for \upchord{Ab7}me
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
It's \upchord{C}hard to \upchord{A7}pass the \upchord{Dm}time a- \upchord{G7}-way
\upchord{C}I'm in a \upchord{A7}dangerous \upchord{D7}mood I \upchord{G7}say
I've \upchord{C}smoked two \upchord{C7}cigar- \upchord{F}-ettes to- \upchord{Ab7}-day
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
\upchord{C}First I \upchord{A7}stand and \upchord{Dm}then I \upchord{G7}sit
\upchord{C}Then I \upchord{A7}sit and \upchord{D7}stand a \upchord{G7}bit
But \upchord{C}I can't \upchord{C7}stand much \upchord{F}more of \upchord{Ab7}it
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
&nbsp;
We're \upchord{C7}parted from each other, \upchord{F}and that's too bad
\upchord{D7}You're my favourite mother, oh the best I ever \upchord{G7}had
&nbsp;
\upchord{C}I got \upchord{A7}such an \upchord{Dm}awful \upchord{G7}shock
I \upchord{C}asked the \upchord{A7}time, for \upchord{D7}there's no \upchord{G7}clock
And the \upchord{C}warder \upchord{C7}said &quot;Six \upchord{F}months, old \upchord{Ab7]
cock!&quot;
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
I \upchord{C}ordered \upchord{A7}lunch from \upchord{Dm}soup to \upchord{G7}sweet
but \upchord{C}they foR- \upchord{A7}-got the \upchord{D7}fish and \upchord{G7}meat
And \upchord{C}since the \upchord{C7}soup there's \upchord{F}nowt to \upchord{Ab7}eat
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
\upchord{C}I've had \upchord{A7}such a \upchord{Dm}tummy \upchord{G7}ache
\upchord{C}All night \upchord{A7}long I've \upchord{D7}been a- \upchord{G7}-wake
Some \upchord{C}castor \upchord{C7}oil they \upchord{F}made me \upchord{Ab7}take
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
&nbsp;
We're \upchord{C7}parted from each other, \upchord{F}and that's too bad
\upchord{D7}You're my favourite mother, oh the best I ever \upchord{G7}had
&nbsp;
\upchord{C}I've played \upchord{A7}&quot;Peter, \upchord{Dm}fly away \upchord{G7]
Paul&quot;
\upchord{C}I've played \upchord{A7}tiddlywinks \upchord{D7}an' \upchord{G7}all
I've \upchord{C}written rude \upchord{C7}words up- \upchord{F}-on the \upchord{Ab7}wall
Oh \upchord{G7}Mother what'll I do \upchord{C}now?
&nbsp;
<h3>Instrumental:</h3>
\upchord{C}\upchord{C}\upchord{G7}\upchord{G7}\upchord{C}\upchord{C}\upchord{G7}\upchord{G7]
\upchord{C}\upchord{C7}\upchord{F}\upchord{Ab7}\upchord{G7}\upchord{Ab7}\upchord{G7}\upchord{C]
&nbsp;
<h5>(Ab7 is basically G7 played one fret higher and with the top string
fingered at the 1st fret.)</h5>
<h6>(In George Formby's recorded version the word &quot;Hell&quot; is replaced
by a humorous parping noise. Modern sensibilities being what they are we could
consider this optional)</h6>
