\section{Echo Beach / (Martha and the Muffins)}\label{sec:echo_beach}
\upchord{Am}\upchord{G}\upchord{Em}\upchord{F}\upchord{G}x 4
\\
I \upchord{Am}know it's out of fashion, \upchord{D}and a \upchord{C}trifle \upchord{Am]
uncool, \upchord{D}\upchord{Em]
But \upchord{Am}I can't help it, \upchord{D}I'm a \upchord{C}romantic \upchord{Am}fool.
\upchord{D}\upchord{Em]
It's a \upchord{Am}habit of mine \upchord{D}to watch the \upchord{C}sun go \upchord{Am]
down. \upchord{D}\upchord{Em]
On \upchord{Am}Echo Beach, \upchord{D}I watch the \upchord{C}sun go \upchord{Am}down.
\upchord{D}\upchord{Em]
\\
\textbf{Chorus}
From \upchord{G}9 to five I have to spend my \upchord{D}time at work.
My \upchord{G}job is very boring I'm an \upchord{D}office clerk.
The \upchord{Am}only thing that helps me pass the \upchord{Em}time away
Is \upchord{Am}knowing I'll be back in Echo \upchord{Em}Beach some day.
\\
(with saxophone)
\upchord{Am}\upchord{G}\upchord{Em}\upchord{F}\upchord{G}x 4
\\
On \upchord{Am}silent summer evenings \upchord{D}the sky's \upchord{C}alive with
\upchord{Am}light. \upchord{D}\upchord{Em]
A \upchord{Am}building in the distance - \upchord{D}surreal \upchord{C}istic \upchord{Am]
sight. \upchord{D}\upchord{Em]
On \upchord{Am}Echo Beach, \upchord{D}waves make the \upchord{C}only \upchord{Am}sound.
\upchord{D}\upchord{Em]
On \upchord{Am}Echo Beach, \upchord{D}there's not a \upchord{C}soul a \upchord{Am}round.
\upchord{D}\upchord{Em]
\\
\textbf{Chorus}
From \upchord{G}9 to five I have to spend my \upchord{D}time at work.
My \upchord{G}job is very boring I'm an \upchord{D}office clerk.
The \upchord{Am}only thing that helps me pass the \upchord{Em}time away
Is \upchord{Am}knowing I'll be back in Echo \upchord{Em}Beach some day.
\\
\upchord{F}\upchord{G}\upchord{Bflat}\upchord{C}x 2
\\
\upchord{Am}Echo Beach \upchord{G}far away in time, \upchord{Em}Echo Beach \upchord{F]
far away \upchord{G}in time...
\textbf{(repeat ad neauseam)}
